### 2021-02-24 preliminaries.tex
Improve Preliminaries

The common saturation-based \glspl{atp} structure the proof search
by maintaining two classes of the inferred clauses: processed and unprocessed \cite{10.1007/978-3-030-29436-6_29}.
In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
is selected from the unprocessed set
and all the inferences between the given clause and the processed clauses are performed.
The resulting new clauses are added to the unprocessed set.

\todo{MS: Celkove hezky! Jen mi tu nejak chybi konec... A taky proc se to vsechno rika.
V PAAR clanku, pokud si dobre vzpominam, bylo hlavnim cilem zavest znaceni pro
 ``pocet iteraci nez se najde dukaz''. aby se pak pouzilo dale\dots
Nicmene ctu ted beginning->end, tak nevim, co chystas dale. }

@@

The \emph{\acrfull{kbo}}, a commonly used simplification ordering scheme,
is parameterized by symbol weights and a \emph{symbol precedence},
a permutation of the non-logical symbols of the input problem.
In this work we focus on finding a symbol precedence which 
leads to a good performance of an ATP
when plugged into the \gls{kbo},
leaving all the symbol weights at the default 
value 1 as set by the \gls{atp} \Vampire{}.

@@

A \emph{feedforward \acrlong{ann}} \cite{DBLP:books/daglib/0040158} is a \acrlong{dag} of \emph{modules}.
Each module is an operation that consumes a numeric (input) \emph{vector} and outputs a numeric vector.
Each of the components of the output vector is called a \emph{unit} of the module.
The output of each module is differentiable with respect to the input.
\todo{MS: mozna bych byl opetrnejsi. Co ReLU a derivace v bode zlomu? ;)}

@@

\todo{MS: Hezke! Ted uz v arichtekture muzes mavat pojmy o neuronkach a bude to tu uktovne! }

>>>>

%The common saturation-based \glspl{atp} structure the proof search
Since the space of the derivable clauses is typically very large,
the efficacy of the prover depends on the order in which the inferences are applied.
The common saturation-based \glspl{atp} order the inferences
by maintaining two classes of the inferred clauses: processed and unprocessed \cite{10.1007/978-3-030-29436-6_29}.
In each \emph{iteration of the saturation loop}, one clause (so-called \emph{given clause})
is selected from the unprocessed set
and all the inferences between the given clause and the processed clauses are performed.
The resulting new clauses are added to the unprocessed set.

\todo{MS: Celkove hezky! Jen mi tu nejak chybi konec... A taky proc se to vsechno rika.
V PAAR clanku, pokud si dobre vzpominam, bylo hlavnim cilem zavest znaceni pro
 ``pocet iteraci nez se najde dukaz''. aby se pak pouzilo dale\dots
Nicmene ctu ted beginning->end, tak nevim, co chystas dale.\\
FB: Doplnil jsem motivaci do prvni vety odstavce.}

@@

The \emph{\acrfull{kbo}}, a commonly used simplification ordering scheme,
is parameterized by symbol weights and a \emph{symbol precedence},
a permutation of the non-logical symbols of the input problem.
In this work we focus on the task of finding a symbol precedence which
leads to a good performance of an ATP
when plugged into the \gls{kbo},
leaving all the symbol weights at the default 
value 1 as set by the \gls{atp} \Vampire{}.

@@

A \emph{feedforward \acrlong{ann}} \cite{DBLP:books/daglib/0040158} is a \acrlong{dag} of \emph{modules}.
Each module is an operation that consumes a numeric (input) \emph{vector} and outputs a numeric vector.
Each of the components of the output vector is called a \emph{unit} of the module.
The output of each module is differentiable with respect to the input almost everywhere.
\todo{FB: Should we explain why "almost everywhere" suffices?}

@@
